Re-examining cross-cultural similarity judgements using lexical co-occurrence

### 2023-01-01 code/4_paper/manuscript/manuscript.Rmd
fixed manuscript

```{r add cosine linguistic model to Ji et al., include=FALSE, cache = T}
fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

@@

```{r add linguistic model to Ji et al., include=FALSE}
fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

@@

```{r country language interaction in cosine prop, include = F}
fit.language_cos = glmer(responses_theme ~ theme_cosine_prop_corr_lang + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(triad %in% triads_omit)),  
          family="binomial")
summary(fit.language_cos)
fit.language_cos.anova = Anova(fit.language_cos, type = 3)
fit.language_cos.anova

fit.country_language_cos= glmer(responses_theme ~ theme_cosine_prop_corr_lang * country + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(triad %in% triads_omit)),  
          family="binomial")
summary(fit.country_language_cos)
fit.country_language_cos.anova = Anova(fit.country_language_cos, type = 3)
fit.country_language_cos.anova

>>>>

@@

```{r add linguistic model to Ji et al., include=FALSE, eval = F}
# this is probably similar to Q3
fit.country = glmer(responses_theme ~ country + (1 | subject) + (1 | triad), 
                           data = df %>% filter(country != "Vietnam"), 
                           family = "binomial")

@@

```{r country language interaction in cosine prop, include = F}
fit.language_cos = glmer(responses_theme ~ theme_cosine_prop_corr_lang + (1 | subject) + (1 | triad), 
          data = df,  
          family="binomial")
summary(fit.language_cos)
fit.language_cos.anova = Anova(fit.language_cos, type = 3)
fit.language_cos.anova

fit.country_language_cos= glmer(responses_theme ~ theme_cosine_prop_corr_lang * country + (1 | subject) + (1 | triad), 
          data = df,  
          family="binomial")
summary(fit.country_language_cos)
fit.country_language_cos.anova = Anova(fit.country_language_cos, type = 3)
fit.country_language_cos.anova
